---
title: "sold_units_ml"
author: "Jerónimo Pissinis"
date: "2/21/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```


## Analysis of the factors related with the number of units sold per year

```{r , echo=TRUE}
#Importing the packages
library(readr)
library(car)
library(glmnet)
library(leaps)
```


Importing the data
```{r , echo=TRUE}
file_path<-"../raw/sold_units_final.csv"
sold_units<-read_csv(file_path)

#Dropping the year column, inflation and devaluación.
sold_units<-sold_units[,2:9]

#Centering the variables to reduce structural multicolinearity
sold_units[,6]<-scale(sold_units[,6],scale=FALSE)
sold_units[,7]<-scale(sold_units[,7],scale=FALSE)
sold_units[,8]<-scale(sold_units[,8],scale=FALSE)


#Renaming the columns
my_names<-c("num_units","itcrb","import_restriction","semiconductor_crisis",
            "brecha_cambiaria", "reserves","PIB","PIB_over_reserves")
names(sold_units)<-my_names
```


Building the model
```{r , echo=TRUE}
sold_units_selected<-lm(sold_units)
summary(sold_units_selected)
```


Pairwise plots of the features
```{r , echo=TRUE}
pairs(sold_units)
```

Analyzing the residuals
```{r , echo=TRUE}
plot(fitted(sold_units_selected),residuals(sold_units_selected))
qqnorm(residuals(sold_units_selected))
```


Looking for outliers and high leverage points
```{r , echo=TRUE}
plot(fitted(sold_units_selected),rstandard(sold_units_selected))
plot(hatvalues(sold_units_selected))
abline(h=length(coef(sold_units_selected))/nrow(sold_units)*2, 
       col = "red",lty = 2)
plot(rstandard((sold_units_selected)))
```


Looking for colinearity
Correlation matrix
```{r , echo=TRUE}
cor(sold_units[,-1])
```

Variance inflation factors
```{r , echo=TRUE}
vif(sold_units_selected)
```

Eigenvalues of the correlation matrix
```{r , echo=TRUE}
eigen(cor(sold_units[,-1]))
```

# Feature selection
Applying best subset selection
```{r , echo=TRUE}
sold_units_subsets<-regsubsets(sold_units$num_units~.,sold_units,nvmax = 10)
summary(sold_units_subsets)
plot(summary(sold_units_subsets)$adjr2)
plot (sold_units_subsets, scale = "adjr2")
which.max(summary(sold_units_subsets)$adjr2)
coef(sold_units_subsets, which.max(summary(sold_units_subsets)$adjr2))
```

Building the selected model
```{r , echo=TRUE}
sold_units_selected<-
  lm(sold_units[,names(sold_units)%in%
    c("num_units",names(coef(sold_units_subsets,
                             which.max(summary(sold_units_subsets)$adjr2))))])
summary(sold_units_selected)
```

Building the model with 5 predictors
```{r , echo=TRUE}
sold_units_selected<-
  lm(sold_units[,names(sold_units)%in%
                  c("num_units",names(coef(sold_units_subsets,5)))])
summary(sold_units_selected)
```
Analyzing the residuals
```{r , echo=TRUE}
plot(fitted(sold_units_selected),residuals(sold_units_selected))
qqnorm(residuals(sold_units_selected))
```

Looking for outliers and high leverage points
```{r , echo=TRUE}
plot(fitted(sold_units_selected),rstandard(sold_units_selected))
plot(hatvalues(sold_units_selected))
abline(h=length(coef(sold_units_selected))/nrow(sold_units)*2, 
       col = "red",lty = 2)
plot(rstandard((sold_units_selected)))
```

Looking for colinearity
Variance inflation factors
```{r , echo=TRUE}
vif(sold_units_selected)
```