---
title: "sold_units_complete"
author: "Francisco Finochietto and Jerónimo Pissinis"
date: "2/27/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Analysis of the factors related with the number of units sold per year

```{r , echo=TRUE}
#Importing the packages
library(readr)
library(car)
library(glmnet)
library(leaps)
library(lmvar)
```


Importing the data
```{r , echo=TRUE}
file_path<-"../raw/sold_units_complete.csv"
sold_units<-read_csv(file_path)

#Dropping the year column.
sold_units<-sold_units[,-1]

#Centering the variables to reduce structural multicolinearity
sold_units[,8]<-scale(sold_units[,8],scale=FALSE)
sold_units[,9]<-scale(sold_units[,9],scale=FALSE)
sold_units[,10]<-scale(sold_units[,10],scale=FALSE)

#Renaming the columns
my_names<-c("num_units", "itcrb", "imported_cars", "semiconductor_crisis",
            "devaluacion_interanual", "inflation", "import_restriction",
            "PIB", "reserves", "PIB_over_reserves", "exchange_difference",
            "industry_trade_balance_difference")
names(sold_units)<-my_names
```


Building the model
```{r , echo=TRUE}
sold_units_model<-lm(sold_units, y= TRUE, x = TRUE)
summary(sold_units_model)
```


Pairwise plots of the features
```{r , echo=TRUE}
pairs(sold_units)
```

Analyzing the residuals
```{r , echo=TRUE}
plot(fitted(sold_units_model),residuals(sold_units_model))
qqnorm(residuals(sold_units_model))
```


Looking for outliers and high leverage points
```{r , echo=TRUE}
plot(fitted(sold_units_model),rstandard(sold_units_model))
plot(hatvalues(sold_units_model))
abline(h=length(coef(sold_units_model))/nrow(sold_units)*2, 
       col = "red",lty = 2)
high_leverage_points<-hatvalues(sold_units_model)>
  (length(coef(sold_units_model))/nrow(sold_units)*2)
plot(rstandard(sold_units_model), 
     col = factor(high_leverage_points))
```


Looking for colinearity
Correlation matrix
```{r , echo=TRUE}
cor(sold_units[,-1])
```

Variance inflation factors
```{r , echo=TRUE}
vif(sold_units_model)
```

Eigenvalues of the correlation matrix
```{r , echo=TRUE}
eigen(cor(sold_units[,-1]))$values
```

Testing the model using cross-validation
```{r , echo=TRUE}
cv_sold_units<-cv.lm(sold_units_model, k=5,)
cv_sold_units
```

# Feature selection
Applying best subset selection
```{r , echo=TRUE}
sold_units_all<-regsubsets(sold_units$num_units~.,sold_units,nvmax = 12)
summary(sold_units_all)
plot(summary(sold_units_all)$adjr2)
plot(sold_units_all, scale = "adjr2")
best_adjr2<-which.max(summary(sold_units_all)$adjr2)
subset_coef<-names(coef(sold_units_all, best_adjr2))
```

Building the selected model
```{r , echo=TRUE}
sold_units_subset<-
  lm(sold_units[,names(sold_units)%in%
    c("num_units",subset_coef)], y = TRUE, x = TRUE)
summary(sold_units_subset)
```


Analyzing the residuals
```{r , echo=TRUE}
plot(fitted(sold_units_subset),residuals(sold_units_subset))
qqnorm(residuals(sold_units_subset))
```

Looking for outliers and high leverage points
```{r , echo=TRUE}
plot(fitted(sold_units_subset),rstandard(sold_units_subset))
plot(hatvalues(sold_units_subset))
abline(h=length(coef(sold_units_subset))/nrow(sold_units)*2, 
       col = "red",lty = 2)
high_leverage_points<-hatvalues(sold_units_subset)>
  (length(coef(sold_units_subset))/nrow(sold_units)*2)
plot(rstandard(sold_units_subset), 
     col = factor(high_leverage_points))
```

Looking for colinearity
Correlation matrix and its eigen values
```{r , echo=TRUE}
subset_coef_cor<-cor(sold_units[,names(sold_units)%in%subset_coef])
subset_coef_cor
eigen(subset_coef_cor)$values
```

Variance inflation factors
```{r , echo=TRUE}
vif(sold_units_subset)
```

Removing the high leverage outlier
```{r , echo=TRUE}
sold_units_subset_rm<-
  lm(sold_units[!(high_leverage_points &
                    (rstandard(sold_units_subset)>2)),
                  names(sold_units)%in% c("num_units",subset_coef)], 
     y = TRUE, x = TRUE)
summary(sold_units_subset_rm)
summary(sold_units_subset)
vif(sold_units_subset_rm)
```

Testing the model selected with best subset selection using cross-validation
```{r , echo=TRUE}
cv_sold_units_subset<-cv.lm(sold_units_subset, k=5,)
cv_sold_units_subset
```

Applying LASSO
```{r , echo=TRUE}
sold_units_lasso<-glmnet(as.matrix(sold_units[,-1]),
                         as.matrix(sold_units[,1]),alpha=1)
sold_units_lasso
#selecting lambda using cross-validation
cv_sold_units_lasso<- cv.glmnet(as.matrix(sold_units[,-1]),
                                as.matrix(sold_units[,1]),
                                type.measure = c("mse"),
                                alpha=1,nfolds = 5)
cv_sold_units_lasso
plot(cv_sold_units_lasso)
best_lambda <- cv_sold_units_lasso$lambda.min
sold_units_lasso_best<-glmnet(as.matrix(sold_units[,-1]), 
                              as.matrix(sold_units[,1]), alpha = 1,
                              lambda = best_lambda)
sold_units_lasso_best
coef(sold_units_lasso_best)
```

Comparing the MSE of the best subset and LASSO models
```{r , echo=TRUE}
mse_lasso<-min(cv_sold_units_lasso$cvm)
mse_subset<-cv_sold_units_subset$MSE$mean
mse_lasso
mse_subset
sqrt(mse_lasso)
sqrt(mse_subset)
```